%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}

        \if\relax\detokenize{#2}\relax
            % nothing
        \else
            $|$ \small{#2}
        \fi

        & \textbf{\small #3} \\
        {\small#4} & {\small #5} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Saurabh Singh Kushwah} \\ \vspace{1pt}
    Pune, India \\ \vspace{1pt}
    \small \raisebox{-0.1\height}
        \faPhone\ 920-968-1432 ~
        % \href{https://saurabhkushwah.com/}{\raisebox{-0.2\height}\faLink\ saurabhkushwah.com}  ~
        \href{mailto:saurabh.singh.kushwah.1999@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ saurabh.singh.kushwah.1999@gmail.com} ~
        \href{https://linkedin.com/in/saurabh-kushwah/}{\raisebox{-0.2\height}\faLinkedin\ saurabh-kushwah}  ~
    \vspace{-8pt}
\end{center}

% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Data Structures
%                 \item Software Methodology
%                 \item Algorithms Analysis
%                 \item Database Management
%                 \item Artificial Intelligence
%                 \item Internet Technology
%                 \item Systems Programming
%                 \item Computer Architecture
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd

% Druva
%     1. Support Database Workload
%     2. Daintree RBAC & Product Telemetry
%     3. UDA Support
%     4. Session Enhancements
%     5. AWS Nighlty
%     6. COGS Program
%     7. Resty Bug

% Persistent Systems
%     1. Report Framework
%     2. Link/DeLink Paperwork
%     3. Dynamic Role Based Menu


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Druva Data Solutions}{Go, AWS, Distributed Systems}{Jun 2022 -- Current}
      {Staff Software Engineer}{Pune, IN}
      \resumeItemListStart
        \resumeItem{\textbf{Daintree Team}: Working on Druva's next-generation storage system. Managing data, deduplication, and file systems.}
        \resumeItem{\textbf{CloudCache Development}: Contributed to the development of CloudCache, an on-premise software appliance that optimizes backup and restores. \textbf{Reduced backup and restore time by 30\%}, improving data protection and minimizing downtime.\textbf{(Go, Channels)}}
        \resumeItem{\textbf{Ransomware Recovery}: Contributed to the development \textbf{\href{https://docs.druva.com/Cyber_Resilience/Ransomware_Recovery/Quarantine_Bay}{\raisebox{-0.2\height}Quarantine Bay\ \faLink}} feature to effectively isolate and contain infected components during a ransomware attack. This feature aims to prevent the spread of infection by isolating and containing the affected parts.}
        \resumeItem{\textbf{Body Swap Bug}: Identified and resolved a crucial bug in the HTTP client package, rectifying issues related to request body swaps and data corruption. Introduced verification measures across all APIs as a temporary solution until the underlying package bug was fixed.}
        \resumeItem{\textbf{AWS E2E Pipeline}: Designed end-to-end infrastructure and pipeline systems for testing on AWS, establishing the standard approach for testing pre-production releases seamlessly, eliminating the need for manual intervention. \textbf{(Python, AWS SSM)}}
      \resumeItemListEnd

    \resumeSubheading
      {Persistent Systems}{Java, Spring Boot, Micro Service}{Jul 2021 -- Jun 2022}
      {Software Engineer}{Pune, IN}
      \resumeItemListStart
        \resumeItem{Contributing to the development of an ERP system for \textbf{BlueDart}, the largest courier company in India.}
        \resumeItem{\textbf{Report System}: Designed and implemented a comprehensive reporting system that currently supports over 100 reports and their corresponding APIs}
        \resumeItem{\textbf{Role Based Menu}: Designed and implemented a dynamic, role-based menu system that generates a user interface menu based on individual roles and dynamically adapts to changes in user privileges.\textbf{(IAM, K8 ConfigMap)}}
        \resumeItem{\textbf{Link/DeLink Paperwork}: Engineered a feature facilitating the linking and delinking of packages upon arrival at any pickup location. Integrated external shipping APIs seamlessly using asynchronously.\textbf{(Async Java)}}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Rust, Java, Python, C, SQL, Shell} \\
     \textbf{AWS}{: DDB, S3, ECS, SQS, RDS, SSM} \\
     \textbf{Tools}{: Linux, Docker, Kubernetes, Jenkins, Git} \\
     \textbf{Web}{: Go-Kit, Tokio, Spring Boot} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------AWARDS-----------
\section{Awards}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Druva Company-Wide Hackathon Winner - AI Assistant} \textbf{\href{https://saurabhkushwah.com/static/documents/hackathon-winner-2023.pdf}{\faLink}} $|$ {Go, Shell, Google DialogFlow}}{Jan 2023}
          \resumeItemListStart
            \resumeItem{Led winning team in Druva's company-wide hackathon with 200+ participants.}
            \resumeItem{Developed an AI-powered support assistant that automated customer data analysis, eliminating the need for support staff to seek developer assistance.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{All Stars Awards} \textbf{\href{https://saurabhkushwah.com/static/documents/all-stars-award.pdf}{\faLink}} $|$ {Go, Shell}}{Jun 2023}
          \resumeItemListStart
            \resumeItem{Received recognition for outstanding efforts in achieving FedRAMP compliance for the project.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{High Five - Individual Awards} \textbf{\href{https://saurabhkushwah.com/static/images/high-five-award.png}{\faLink}} $|$ {Java, Spring Boot}}{Mar 2022}
          \resumeItemListStart
            \resumeItem{Received an award in recognition of successfully managing multiple features independently, executing them in parallel, and consistently meeting deadlines.}
          \resumeItemListEnd
          % \vspace{-13pt}
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Full-Text Search Engine} $|$ {Go, Inverted Index}}{Apr 2021}
          \resumeItemListStart
            \resumeItem{Developed FTS engine able to search across thousands of documents in less than a millisecond.}
            \resumeItem{FTS engine extended to support more sophisticated boolean queries by utilizing a multi-stage process encompassing tokenizer, filters, stop words removal, and stemming to construct the Inverted Index.}
          \resumeItemListEnd
          % \vspace{-13pt}
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Savitribai Phule Pune University}{}{Jun. 2017 -- Jun 2021}
      {Bachelor of Engineering in Computer Science}{Pune, IN}
  \resumeSubHeadingListEnd

% % %------RELEVANT COURSEWORK-------
% \section{Interests}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Data Structures
%                 \item Distributed Systems
%                 \item Operating Systems
%                 \item Compilers
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd

\end{document}
